Supplementary Information

### 2024-07-03 supplement.Rmd
improved intro and discussion

---
title: "Can Exposure To Forgiving AI Foster Cooperative Play?"
subtitle: "Supplementary Information"

@@

We estimated a three-state model for investor's behaviour, using maximum likelihood estimation via the Expectation-Maximisation algorithm as implemented in the depmixS4 (Visser & Speekenbrink) package for R. The model was estimated using investments from existing datasets of human dyads playing 10 rounds of the RTG with the same trustee. The dataset consisted of a total of 381 games from two data sources: First, a total of 93 repeated trust games with healthy investors and a mix of healthy trustees and trustees diagnosed with Borderline Personality Disorder (BPD) [@king-casas_rupture_2008]. The second source was from data collected as part of a project investigating social exchanges at the Montague lab at Virginia Tech and consists of 288 games.

## Mixed-effects model results for participant returns

>>>>

---
title: "Supplementary Information"
subtitle: ""

@@

We estimated a three-state model for investor's behaviour, using maximum likelihood estimation via the Expectation-Maximisation algorithm as implemented in the depmixS4 package for R [@visser_depmixs4_2021]. The model was estimated using investments from existing datasets of human dyads playing 10 rounds of the RTG with the same trustee. The dataset consisted of a total of 381 games from two data sources: First, a total of 93 repeated trust games with healthy investors and a mix of healthy trustees and trustees diagnosed with Borderline Personality Disorder (BPD) [@king-casas_rupture_2008]. The second source was from data collected as part of a project investigating social exchanges in BPD and antisocial personality disorder reported on elsewhere [@euler_interpersonal_2021; @huang_multidirectional_2020; @rifkin-zybutz_impaired_2021] and consists of 288 games. In both datasets, the investor on which we modelled the HMM's strategy was always selected from a healthy population and the trustees were a mix of healthy participants and those with personality disorders allowing for a diversified interaction behavior.

## Mixed-effects models for participant returns
